Inferring true changes in microbial abundance from taxonomically-biased microbiome measurements

### 2022-01-19 index.Rmd
Adjust git file tracking
Add folders to ignore list and set up index.Rmd so that untracked,
unstaged, and staged files are output in the Preface.
Revise title
Update preface and readme

---
title: "Accurate inference of microbial differential abundance from taxonomically-biased microbiome measurements"
author:
  - Michael R. McLaren^[North Carolina State University; send correspondence to m.mclaren42@gmail.com]
  - Jacob T. Nearing^[Dalhousie University]
  - Amy D. Willis^[University of Washington]
  - Karen G. Lloyd^[University of Tennessee]
  - Benjamin J. Callahan^[North Carolina State University]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
# description:
# For pandoc latex processing
documentclass: article
geometry:
  - top=1in
  - bottom=1in
  - left=1.5in
  - right=1.5in
output:
  bookdown::gitbook:
    css: style.css
    number_sections: true
    includes:
      in_header: header.html
    config:
      sharing:
        facebook: no
        github: yes
        twitter: no
        linkedin: no
        weibo: no
        instapaper: no
        vk: no
        all: ['facebook', 'twitter', 'linkedin', 'weibo', 'instapaper']
  bookdown::pdf_book:
    includes:
      in_header: latex/preamble.tex
    keep_tex: true
    dev: "pdf"
    papersize: letter
    toc_depth: 2
    toc_unnumbered: yes
    toc_appendix: yes
---

@@

```{r}
if (length(status$unstaged) > 0)
  print(status$unstaged)
```

@@

This manuscript addresses the effect that the taxonomic bias inherent in microbiome measurement has on microbial differential-abundance analysis.
We describe the basic problem posed by taxonomic bias for measuring changes in the abundance of particular taxa across conditions and describe new strategies for mitigating the errors it induces.
Analyses of both relative and absolute abundances are considered.
In its current form, the manuscript sits somewhere between a standard scientific article and a monograph; 
it consists of an article followed by a series of appendices which together give a comprehensive treatment of the implications of the @mclaren2019cons model of taxonomic bias for differential-abundance analysis and experimental design.
It is licensed under a [CC BY 4.0 License](https://creativecommons.org/licenses/by/4.0/).
See [the Zenodo record](https://doi.org/10.5281/zenodo.4552717) for how to cite the latest version.

>>>>

---
title: "Inferring true changes in microbial abundance from taxonomically-biased microbiome measurements"
author:
  - Michael R. McLaren^[North Carolina State University; send correspondence to m.mclaren42@gmail.com]
  - Jacob T. Nearing^[Dalhousie University]
  - Amy D. Willis^[University of Washington]
  - Karen G. Lloyd^[University of Tennessee]
  - Benjamin J. Callahan^[North Carolina State University]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
# description:
# For pandoc latex processing
documentclass: article
geometry:
  - top=1in
  - bottom=1in
  - left=1.5in
  - right=1.5in
output:
  bookdown::gitbook:
    css: style.css
    number_sections: true
    includes:
      in_header: header.html
    config:
      sharing:
        facebook: no
        github: yes
        twitter: no
        linkedin: no
        weibo: no
        instapaper: no
        vk: no
        all: ['facebook', 'twitter', 'linkedin', 'weibo', 'instapaper']
  bookdown::pdf_book:
    includes:
      in_header: latex/preamble.tex
    keep_tex: true
    dev: "pdf"
    papersize: letter
    toc_depth: 2
    toc_unnumbered: yes
    toc_appendix: yes
---

@@

```{r}
print(status)
```

@@

This manuscript addresses the effect that the taxonomic bias inherent in microbiome measurement has on microbial differential-abundance analysis.
We describe the basic problem posed by taxonomic bias for measuring changes in the abundance of particular taxa across conditions and describe new strategies for mitigating the errors it induces.
Analyses of both relative and absolute abundances are considered.
The manuscript is licensed under a [CC BY 4.0 License](https://creativecommons.org/licenses/by/4.0/).
See [the Zenodo record](https://doi.org/10.5281/zenodo.4552717) for how to cite the latest version.
